\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin = 1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Joseph Tyler Lariscy - CV }}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Joseph Tyler Lariscy:  CV (Curriculum Vitae)},
            pdfauthor={Joseph Tyler Lariscy},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Joseph Tyler Lariscy}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Associate Professor, Department of
Sociology, Texas A\&M University}
\moveleft.5\hoffset\centerline{351 WCSS · 2935 Research Parkway, Suite
311 · College Station, TX 77843}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:jlariscy@tamu.edu}{\nolinkurl{jlariscy@tamu.edu}}} \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/josephlariscy}{\tt josephlariscy} \hspace{1 mm}      } 

\vspace{2 mm}

\hrule


~

\section{Employment}\label{employment}

\emph{Texas A\&M University}

\setlength{\leftskip}{1cm}

Associate Professor, Department of Sociology \hfill 2024--present\\
Associate Director, Texas Federal Statistical Research Data Center
\hfill 2025--present\\
Faculty Affiliate, Race and Ethnic Studies Institute (RESI)
\hfill 2024--present

\setlength{\leftskip}{0cm}

\emph{University of Texas at Austin}

\setlength{\leftskip}{1cm}

External Faculty Affiliate, Population Research Center
\hfill 2024--present

\setlength{\leftskip}{0cm}

\emph{University of Memphis}

\setlength{\leftskip}{1cm}

Associate Professor, Department of Sociology \hfill 2021--2024\\
Assistant Professor, Department of Sociology \hfill 2015--2021\\
Director of Graduate Studies, Department of Sociology \hfill 2020--2024

\setlength{\leftskip}{0cm}

\emph{Duke University}

\setlength{\leftskip}{1cm}

NIA Postdoctoral Fellow, Duke Population Research Institute
\hfill 2013--2015

\setlength{\leftskip}{0cm}

~

\section{Education}\label{education}

PhD ~ ~Sociology ~ ~ University of Texas at Austin \hfill 2013\\
MA ~ ~ Sociology ~ ~ University of Texas at Austin \hfill 2009\\
BA ~ ~ ~Sociology ~ ~ University of Georgia \hfill 2007

~

\section{Publications}\label{publications}

* = student coauthor

Lariscy, Joseph T. and Israt Jahan.* (2025).
\href{https://www.tandfonline.com/doi/full/10.1080/19485565.2024.2448941}{Sex-Specific
Trends in Educational Attainment and Self-Rated Health, 1972--2018.}
\emph{Biodemography and Social Biology} 70(1): 57--64.

Lariscy, Joseph T. (2025).
\href{https://osf.io/preprints/socarxiv/mc6hv/}{Demographic Methods.} In
\emph{The Wiley-Blackwell Encyclopedia of Health, Illness, Behavior, and
Society, Second Edition.} William C. Cockerham, Jonathan Gabe, Stella
Quah, and J. Michael Ryan (eds.). Wiley.

Brown, Dustin C., Joseph T. Lariscy, and Benjamin H. Walker. (2023).
\href{https://read.dukeupress.edu/demography/article/doi/10.1215/00703370-10423884/342894/State-Level-Trends-in-Lifespan-Variability-in-the}{State-Level
Trends in Lifespan Variability in the United States, 1960--2019: A
Research Note.} \emph{Demography} 60(1): 1--14.

Vogelsang, Eric M. and Joseph T. Lariscy. (2020).
\href{https://journals.sagepub.com/doi/full/10.1177/0022146520962456}{Let's
Drink to Being Socially Active: Family Characteristics, Social
Participation, and Alcohol Abuse across Mid- and Later-Life.}
\emph{Journal of Health and Social Behavior} 61(4): 453--469.

Fatema,* Kaniz and Joseph T. Lariscy. (2020).
\href{https://www.sciencedirect.com/science/article/pii/S2352827320302512}{Mass
Media Exposure and Maternal Healthcare Utilization in South Asia}.
\emph{Social Science \& Medicine--Population Health} 11: 100614.

Lariscy, Joseph T., Robert A. Hummer, and Richard G. Rogers. (2020).
\href{https://www.sciencedirect.com/science/article/pii/S1047279720301393}{Lung
Cancer Mortality among Never-Smokers in the United States: Estimating
Smoking-Attributable Mortality with Nationally Representative Data}.
\emph{Annals of Epidemiology} 45: 5--11.

Lariscy, Joseph T., Samia Tasmim,* and Sarah Collins.* (2020).
\href{https://www.researchgate.net/publication/342352707_Racial_and_Ethnic_Disparities_in_Health}{Racial
and Ethnic Disparities in Health}. In \emph{Encyclopedia of Gerontology
and Population Aging}. Danan Gu and Matthew E. Dupre (eds.). Springer
Nature Switzerland AG.

Brown, Dustin C., Joseph T. Lariscy, and Lucie Kalousová. (2019).
\href{https://link.springer.com/article/10.1007/s11113-018-9505-1}{Comparability
of Mortality Estimates from Social Surveys and Vital Statistics Data in
the United States}. \emph{Population Research and Policy Review} 38(3):
371--401.

Lariscy, Joseph T. (2019).
\href{https://www.sciencedirect.com/science/article/pii/S2352827318302118?via\%3Dihub}{Smoking-Attributable
Mortality by Cause of Death in the United States: An Indirect Approach}.
\emph{Social Science \& Medicine--Population Health} 7: 100349.

Lariscy, Joseph T., Robert A. Hummer, and Richard G. Rogers. (2018).
\href{https://read.dukeupress.edu/demography/article/55/5/1855/167925/Cigarette-Smoking-and-All-Cause-and-Cause-Specific}{Cigarette
Smoking and All-Cause and Cause-Specific Adult Mortality in the United
States}. \emph{Demography} 55(5): 1855--1885.

Lariscy, Joseph T. (2017).
\href{https://link.springer.com/article/10.1007/s11113-016-9415-z}{Black-White
Disparities in Adult Mortality: Implications of Differential Record
Linkage for Understanding the Mortality Crossover}. \emph{Population
Research and Policy Review} 36(1): 137--156.

Lariscy, Joseph T., Claudia Nau, Glenn Firebaugh, and Robert A. Hummer.
(2016).
\href{https://read.dukeupress.edu/demography/article/53/1/215/167323/Hispanic-White-Differences-in-Lifespan-Variability}{Hispanic
White Differences in Lifespan Variability in the United States}.
\emph{Demography} 53(1): 215--239.

Lariscy, Joseph T., Robert A. Hummer, and Mark D. Hayward. (2015).
\href{https://read.dukeupress.edu/demography/article/52/1/1/169365/Hispanic-Older-Adult-Mortality-in-the-United}{Hispanic
Older Adult Mortality in the United States: New Estimates and an
Assessment of Factors Shaping the Hispanic Paradox}. \emph{Demography}
52(1): 1--14.

Gorman, Bridget K., Joseph T. Lariscy, and Charisma Kaushik.* (2014).
\href{https://www.sciencedirect.com/science/article/pii/S0277953614000999?via\%3Dihub}{Gender,
Acculturation, and Smoking Behaviors among U.S. Asian and Latino
Immigrants}. \emph{Social Science \& Medicine} 106: 110--118.

Lariscy, Joseph T., Robert A. Hummer, Jessica M. Rath, Andrea C.
Villanti, Mark D. Hayward, and Donna M. Vallone. (2013).
\href{https://academic.oup.com/ntr/article/15/8/1417/1283744}{Race/Ethnicity,
Nativity, and Tobacco Use among U.S. Young Adults: Results from a
Nationally-Representative Survey}. \emph{Nicotine \& Tobacco Research}
15(8): 1417--1426.

Wade,* Becky, Joseph T. Lariscy, and Robert A. Hummer. (2013).
\href{https://link.springer.com/article/10.1007/s11113-013-9275-8}{Racial/Ethnic
and Nativity Patterns of U.S. Adolescent and Young Adult Smoking}.
\emph{Population Research and Policy Review} 32(3): 353--371.

Lariscy, Joseph T. (2011).
\href{https://journals.sagepub.com/doi/full/10.1177/0898264311421369}{Differential
Record Linkage by Hispanic Ethnicity and Age in Linked Mortality
Studies: Implications for the Epidemiologic Paradox}. \emph{Journal of
Aging and Health} 23(8): 1263--1284.

Hummer, Robert A. and Joseph T. Lariscy. (2011).
\href{https://www.researchgate.net/publication/216839888_Educational_Attainment_and_Adult_Mortality}{Educational
Attainment and Adult Mortality}. Chapter 12 (Pp. 241--262) in
\emph{International Handbook of Adult Mortality}. Richard G. Rogers and
Eileen M. Crimmins (eds). Dordrecht, The Netherlands: Springer.

~

\section{Papers in Preparation}\label{papers-in-preparation}

Lariscy, Joseph T. and Aggie Yellow Horse. Cause-of-Death Contributions
to the Hispanic Mortality Paradox.

Lariscy, Joseph T. and Eric M. Vogelsang. Racial/Ethnic Disparities in
Lifespan Variability.

Lariscy, Joseph T., Rafia Akter,* Dustin Brown, and Benjamin Walker.
Trends in Lifespan Variability among Canadian Provinces and Territories.

Suhel, Golam,* Wesley James, and Joseph T. Lariscy. Household Food
Insecurity Status and Chronic Physical Health Conditions among Adults in
the United States, 2019--2023.

~

\section{Grants and Contracts}\label{grants-and-contracts}

\emph{Racial/Ethnic Disparities in Longitudinal Mortality Follow-up
among Older Americans}. Principal Investigator, Joseph Lariscy. Funded
by National Institute on Aging, Network for Innovative Methods in
Longitudinal Aging Studies (NIMLAS) (Award 1 R24 AG077012-01). \$63,893.
2024--2025.

\emph{Delta Revitalization through Innovation, Vision, and Equity
(DRIVE)}. Subcontractor, Joseph Lariscy. Funded by Delta Regional
Authority, U.S. Department of Labor. \$30,000. 2023--2024.

~

\emph{Delta Revitalization through Innovation, Vision, and Equity
(DRIVE)}. Subcontractor, Joseph Lariscy. Funded by Delta Regional
Authority, U.S. Department of Labor. \$40,000. 2023--2024.

\section{Invited Presentations}\label{invited-presentations}

``Conducting Research using Restricted Federal Statistical Data.''
Office for Research and Innovation, University of Texas at San Antonio,
December 4, 2025

``Racial/Ethnic Disparities in Longitudinal Mortality Follow-up among
Older Americans.'' Network for Innovative Methods in Longitudinal Aging
Studies, University of Michigan, January 26, 2024

``State-Level Trends in Lifespan Variability in the United States,
1960--2019.'' Department of Sociology and Center for Family and
Demographic Research, Bowling Green State University, May 2, 2022

``Cigarette Smoking and Cause-Specific Adult Mortality in the United
States.'' Federal Statistical Research Data Center (FSRDC) Presentation
Series (virtual), September 22, 2021

``State-Level Trends in Lifespan Variability in the United States,
1960--2014.'' New Perspectives on Lifespan Inequality webinar (virtual),
Southern Denmark University. January 21, 2021

``Lung Cancer Mortality among Nonsmokers: Estimating
Smoking-Attributable Mortality with Nationally-Representative Data.''
Social Science Research Institute, Duke University. April 26, 2019

``Cigarette Smoking and Cause-Specific Adult Mortality in the United
States.'' Department of Sociology and Center for Demography and
Population Health, Florida State University. November 30, 2017

``Cigarette Smoking and Cause-Specific Adult Mortality in the United
States.'' Department of Sociology and Aging Studies Institute, Syracuse
University. February 21, 2017

``Hispanic-White Disparities in Lifespan Variability in the United
States.'' Department of Sociology, Vanderbilt University. November 28,
2016

``Cigarette Smoking and Cause-Specific Mortality in the United States.''
Population, Health, and Education Center, University of Missouri.
November 10, 2016

``Hispanic-White Differences in Lifespan Variability.'' CUNY Institute
for Demographic Research, City University of New York. May 6, 2016

``Hispanic Adult Mortality in the United States: New Estimates and an
Assessment of Factors Shaping the Hispanic Paradox.'' Department of
Demography, University of Texas at San Antonio. November 10, 2014

``Racial and Ethnic Inequality in Adult Survival in the United States.''
Department of Sociology, Duke University. September 12, 2014

``The Significance of Differential Record Linkage for Understanding
Black-White Survival Inequality.'' Texas Census Research Data Center,
Texas A\&M University. April 18, 2013

~

\section{Selected Presentations at Professional
Meetings}\label{selected-presentations-at-professional-meetings}

\emph{ASA = American Sociological Association, IAPHS = Interdisciplinary
Association for Population Health Sciences, PAA = Population Association
of America, SDA = Southern Demographic Association, SSS = Southern
Sociological Society}

Lariscy, Joseph T. ``Where is Federal Statistical Data Headed? Federal
Statistical Research Data Centers and Changes in the Federal Statistical
System'' (Panel). SDA, October 17, 2025

Lariscy, Joseph T. and Cynthia Cisneros Franco. ``Differential Record
Linkage and Implications for Racial/Ethnic and Foreign-born/Native-born
Disparities in Adult Mortality.'' PAA, April 11, 2025

Lariscy, Joseph T. and Israt Jahan. ``Gender-Specific Trends in
Educational Attainment and Self-Rated Health, 1972--2018'' (poster).
PAA, April 18, 2024

Joseph T. Lariscy and Aggie Yellow Horse. ``Cause-of-Death Contributions
to the Hispanic Advantage in Life Expectancy'' (poster). PAA, April 18,
2024

Joseph T. Lariscy and Aggie Yellow Horse. ``Cause-of-Death Contributions
to the Hispanic Advantage in Life Expectancy.'' SDA, October 19, 2023

Rahman, Samira and Joseph T. Lariscy. ``Religious Affiliation and
Obesity among Immigrants to the United States'' (poster). SDA, October
19, 2023

Bhattacharjee, Purba and Joseph Lariscy. ``The Relationship between Gun
Violence and the Number of Gun Laws among U.S. States.'' SDA, October
20, 2023

Joseph T. Lariscy and Eric Vogelsang. ``Racial/Ethnic Disparities in
Lifespan Variability in the United States, 2019 and 2020.'' (poster).
PAA, April 14, 2023

Joseph T. Lariscy and Eric Vogelsang. ``Racial/Ethnic Disparities in
Lifespan Variability before and during the COVID-19 Pandemic.'' SDA,
October 18, 2022

Joseph T. Lariscy and Eric Vogelsang. ``Racial/Ethnic Disparities in
Life Expectancy and Lifespan Variability in the United States''
(poster). PAA, April 7, 2022

Joseph T. Lariscy and Eric Vogelsang. ``Racial/Ethnic Disparities in
Mortality Compression and Rectangularization in the United States.'' ASA
(virtual), August 9, 2021

Brown, Dustin C., Joseph T. Lariscy, and Benjamin Walker. ``State-Level
Trends in Lifespan Variability in the United States between 1960 and
2014.'' PAA (virtual), May 5, 2021

Brown, Dustin C., Joseph T. Lariscy, and Benjamin Walker. ``State-Level
Trends in Lifespan Variability in the United States between 1960 and
2014.'' Accepted for presentation at 2020 PAA meeting, Washington, DC
(conference canceled due to COVID-19 virus)

Fatema, Kaniz and Joseph T. Lariscy. ``Mass Media Exposure and Maternal
Healthcare Utilization in South Asia.'' Accepted for poster at 2020 PAA
meeting, Washington, DC (conference canceled due to COVID-19 virus)

Vogelsang, Eric and Joseph T. Lariscy. ``Let's Drink to Being Social:
Family Characteristics, Social Participation, and Alcohol Abuse across
Mid- and Later-Life.'' Accepted for presentation at 2020 PAA meeting,
Washington, DC (conference canceled due to COVID-19 virus)

Brown, Dustin C., Joseph T. Lariscy, and Benjamin Walker. ``State-Level
Trends in Lifespan Variability in the United States between 1960 and
2014.'' Accepted for presentation at 2020 SSS meeting, Jacksonville, FL
(conference canceled due to COVID-19 virus)

Brown, Dustin C., Joseph T. Lariscy, and Benjamin Walker. ``State-Level
Trends in Lifespan Variability in the United States between 1960 and
2014.'' IAPHS, Seattle, WA, October 3, 2019

Lariscy, Joseph T, Robert A. Hummer, and Richard G. Rogers. ``Lung
Cancer Mortality among Nonsmokers: Estimating Smoking-Attributable
Mortality with Nationally-Representative Data'' (poster). PAA, Austin,
TX, April 11, 2019

Lariscy, Joseph T, Robert A. Hummer, and Richard G. Rogers. ``Lung
Cancer Mortality among Nonsmokers: Estimating Smoking-Attributable
Mortality with Nationally-Representative Data.'' SDA, Durham, NC,
October 11, 2018

Lariscy, Joseph T. ``Smoking-Attributable Mortality by Cause of Death:
An Indirect Approach.'' PAA, Denver, CO, April 26, 2018

Lariscy, Joseph T. ``Identifying Smoking-Attributable Causes of Death: A
New Application of the Preston-Glei-Wilmoth Model.'' 2017 SDA,
Morgantown, WV, October 27, 2017

Lariscy, Joseph T. ``Paradox by Number: Mortality Compression and
Rectangularization among U.S. Hispanics'' (poster). PAA, Chicago, IL,
April 27, 2017

Lariscy, Joseph T. ``Paradox by Number: Mortality Compression and
Rectangularization among U.S. Hispanics.'' SDA, Athens, GA, October 13,
2016

Brown, Dustin C., Joseph T. Lariscy, and Lucie Kalousova. ``A Comparison
of Mortality Estimates from Multiple Nationally Representative Surveys
and Vital Statistics Data in the United States.'' PAA, Washington, DC,
April 1, 2016

Lariscy, Joseph T., Robert A. Hummer, Richard G. Rogers, and Charles B.
Nam. ``Cigarette Smoking and Cause-Specific Mortality in the United
States.'' PAA, Washington, DC, March 31, 2016

Lariscy, Joseph T., Robert A. Hummer, Richard G. Rogers, and Charles B.
Nam. ``Cigarette Smoking and Cause-Specific Mortality in the United
States.'' SDA, San Antonio, TX, October 15, 2015

Lariscy, Joseph T. ``The Long Plume of Childhood: Cigarette Smoking
throughout the Life Course and Racial/Ethnic Mortality Differentials''
(round table). ASA, San Francisco, CA, August 19, 2014

Lariscy, Joseph T. Implications of Differential Record Linkage for
Understanding the Black-White Mortality Gap'' (poster). PAA, Boston, MA,
May 3, 2014

Lariscy, Joseph T. ``The Significance of Differential Record Linkage for
Understanding Black-White Survival Inequality.'' SDA, Montgomery, AL,
October 25, 2013

Lariscy, Joseph T. ``The Significance of Differential Record Linkage for
Understanding Black-White Survival Inequality.'' ASA, New York, NY,
August 11, 2013

Lariscy, Joseph T., Claudia Nau, Glenn Firebaugh, and Robert A. Hummer.
``Racial and Ethnic Inequality in Adult Survival: Decomposition of Age
at Death Variance among U.S. Adults.'' PAA, New Orleans, LA, April 11,
2013

Lariscy, Joseph T., Claudia Nau, Glenn Firebaugh, and Robert A. Hummer.
``Racial and Ethnic Inequality in Adult Survival: Decomposition of Age
at Death Variance among U.S. Adults.'' SDA, Williamsburg, VA, October
11, 2012

Lariscy, Joseph T. ``The Long Plume of Childhood: Cigarette Smoking
throughout the Life Course and Adult Mortality Differentials.'' PAA, San
Francisco, CA, May 4, 2012

Lariscy, Joseph T. ``The Long Plume of Childhood: Cigarette Smoking
throughout the Life Course and Adult Mortality Differentials.'' SDA,
Tallahassee, FL, October 20, 2011

Lariscy, Joseph T., Kristine Hopkins, and Rachel Samsel. ``Acculturation
and Parent-Adolescent Communication about Sex among Mexican-Origin
Families.'' ASA, Las Vegas, NV, August 20, 2011

Hummer, Robert A., Joseph T. Lariscy, and Mark D. Hayward. ``Hispanic
Adult Mortality in the United States: A Review, New Estimates, and
Comparisons to Other Population Groups.'' MacArthur Foundation Research
Network on an Aging Society, Palo Alto, CA, February 14, 2011

Lariscy, Joseph T. ``Race/Ethnicity and US Adult Mortality: An
Examination of Vital Status Ascertainment in the National Health
Interview Survey Linked Mortality Files.'' SDA, Galveston, TX, October
23, 2009

Lariscy, Joseph T. ``Latino Healthcare Coverage in an Emerging Gateway
Southern State.'' SDA, Durham, NC, November 3, 2006

~

\section{Teaching}\label{teaching}

\emph{Texas A\&M University}

\setlength{\leftskip}{0.5cm}

Graduate:

\setlength{\leftskip}{0cm}
\setlength{\leftskip}{1cm}

SOCI 600: Introduction to Sociological Data Analysis (fall 2026)\\
SOCI 622: Social Demography (spring 2026)\\
SOCI 642: Fertility and Mortality (fall 2024)

\setlength{\leftskip}{0cm}

\setlength{\leftskip}{0.5cm}

Undergraduate:

\setlength{\leftskip}{0cm}
\setlength{\leftskip}{1cm}

SOCI 420: Advanced Methods of Social Research (spring 2025)\\
SOCI 312: Population and Society (fall 2025, spring 2025)

\setlength{\leftskip}{0cm}

\emph{University of Memphis}

\setlength{\leftskip}{0.5cm}

Graduate:

\setlength{\leftskip}{0cm}
\setlength{\leftskip}{1cm}

SOCI 7612: Social Demography (fall 2023, spring 2021, spring 2018)\\
SOCI 7851/8851: Medical Sociology (fall 2016)\\
SOCI 6312: Intermediate Social Statistics (spring 2024, spring 2023,
spring 2022,\\
\strut ~~~~~spring 2021, spring 2020, spring 2019, spring 2018, spring
2017, spring 2016)

\setlength{\leftskip}{0cm}

\setlength{\leftskip}{0.5cm}

Undergraduate:

\setlength{\leftskip}{0cm}
\setlength{\leftskip}{1cm}

SOCI 3311: Social Statistics (fall 2023, spring 2020, fall 2019, fall
2018, fall 2017,\\
\strut ~~~~spring 2017, fall 2016, fall2015)\\
SOCI 3422: Racial and Ethnic Minorities (fall 2022, spring 2019, fall
2018)\\
SOCI 4541: Sociology of Aging (fall 2020)\\
SOCI 4851: Medical Sociology (fall 2022, fall 2019, fall 2017)\\
UNHP 1100: Census 2020: How the United States Counts its Diverse
Population (fall 2019)

\setlength{\leftskip}{0cm}

\emph{University of Texas at Austin}

\setlength{\leftskip}{1cm}

SOC 319: Introduction to Social Demography (fall 2011)

\setlength{\leftskip}{0cm}

~

\section{Honors and Awards}\label{honors-and-awards}

2024-25 ~Scholar Strategy Network Health Equity Scholars Program (HESP)
Cohort

2021 ~ ~ ~ Professional Development Assignment, University of Memphis\\
\strut ~ ~ ~ ~ ~ ~ ~ Research leave for Fall 2021 semester

2020 ~ ~ ~ Open Access Grant; Fine Arts, Humanities, \& Social Science
Pilot Program;\\
\strut ~ ~ ~ ~ ~ ~ ~ University of Memphis\\
\strut ~ ~ ~ ~ ~ ~ ~ \$3,270 for Gold Open Access fees

2015--16 ~Professional Development Support, Carolina Population
Center,\\
\strut ~ ~ ~ ~ ~ ~ ~ University of North Carolina-Chapel Hill\\
\strut ~ ~ ~ ~ ~ ~ ~ \$1,950 to conduct analyses at the Triangle Federal
Statistical Research Data Center

2015 ~ ~ ~ IPUMS Health Surveys Research Award, Minnesota Population
Center\\
\strut ~ ~ ~ ~ ~ ~ ~ \emph{Hispanic Older Adult Mortality in the United
States: New Estimates and an Assessment of}\\
\strut ~ ~ ~ ~ ~ ~ ~ \emph{Factors Shaping the Hispanic Paradox}, with
Robert Hummer and Mark Hayward

2013--15 ~Postdoctoral Fellowship, Duke Population Research Institute\\
\strut ~ ~ ~ ~ ~ ~ ~ T32 Training Grant in the Social, Medical, and
Economic Demography of Aging,\\
\strut ~ ~ ~ ~ ~ ~ ~ funded by the National Institute on Aging

2013 ~ ~ ~ Texas Census Research Data Center Proposal Development Grant
(\$500)\\
\strut ~ ~ ~ ~ ~ ~ ~ \$500 to assist with data linkage fees

2012--13 ~Sociology Continuing Fellowship\\
\strut ~ ~ ~ ~ ~ ~ ~ Dissertation fellowship awarded by University of
Texas Graduate School (\$23,800)

2012 ~ ~ ~ Doug Forbes Research Development Award, awarded by PRC
Training Committee\\
\strut ~ ~ ~ ~ ~ ~ ~ \$1,000 to conduct analyses at the Texas Census
Research Data Center

2011 ~ ~ ~ Everett S. Lee Graduate Student Paper Award\\
\strut ~ ~ ~ ~ ~ ~ ~ \emph{The Long Plume of Childhood: Cigarette
Smoking throughout the Life Course and Adult}\\
\strut ~ ~ ~ ~ ~ ~ ~ \emph{Mortality Differentials}\\
\strut ~ ~ ~ ~ ~ ~ ~ Awarded by the Southern Demographic Association

2011 ~ ~ ~ Doug Forbes Research Development Award\\
\strut ~ ~ ~ ~ ~ ~ ~ Awarded by Population Research Center Training
Committee, University of Texas at\\
\strut ~ ~ ~ ~ ~ ~ ~ Austin\\
\strut ~ ~ ~ ~ ~ ~ ~ \$1,075 award to attend Cells2Society Biomarkers
Institute, Northwestern University

2010--11 ~Ruth L. Kirschstein National Research Service Award
Pre-doctoral Traineeship\\
\strut ~ ~ ~ ~ ~ ~ ~ Traineeship awarded by Population Research Center
Training Committee,\\
\strut ~ ~ ~ ~ ~ ~ ~ University of Texas at Austin and funded by NICHD
(\$22,180)

2007 ~ ~ ~ David Bruton, Jr.~Graduate Fellowship\\
\strut ~ ~ ~ ~ ~ ~ ~ Awarded by Population Research Center Training
Committee, University of Texas at\\
\strut ~ ~ ~ ~ ~ ~ ~ Austin

2007 ~ ~ ~ Elected to Phi Beta Kappa\\
\strut ~ ~ ~ ~ ~ ~ ~ University of Georgia

2005--06 ~President, Alpha Kappa Delta Sociological Honor Society\\
\strut ~ ~ ~ ~ ~ ~ ~ Department of Sociology, University of Georgia

\section{Professional Development}\label{professional-development}

2013--22 ~Research Associate, Federal Statistical Research Data
Centers\\
\strut ~ ~ ~ ~ ~ ~ ~ Special Sworn Status granted July 2013\\
\strut ~ ~ ~ ~ ~ ~ ~ Locations: Texas RDC (College Station, TX),
Triangle RDC (Durham, NC), and\\
\strut ~ ~ ~ ~ ~ ~ ~ Missouri RDC (Columbia, MO)\\
\strut ~ ~ ~ ~ ~ ~ ~ Center for Economic Studies, U.S. Census Bureau,
U.S. Department of Commerce

2016 ~ ~ ~ Workshop on Formal Demography (5 days)\\
\strut ~ ~ ~ ~ ~ ~ ~ Berkeley Population Center and Center on the
Economics and Demography of Aging,\\
\strut ~ ~ ~ ~ ~ ~ ~ University of California, Berkeley

2014 ~ ~ ~ Summer Training Workshop on African American Aging Research
(3 days)\\
\strut ~ ~ ~ ~ ~ ~ ~ Michigan Center for Urban African American Aging
Research, University of Michigan

2012 ~ ~ ~ RAND Summer Institute (4 days)\\
\strut ~ ~ ~ ~ ~ ~ ~ Center for the Study of Aging, RAND Corporation

2012 ~ ~ ~ Stanford Workshop in Formal Demography (3 days)\\
\strut ~ ~ ~ ~ ~ ~ ~ Institute for Research in the Social Sciences,
Stanford University

2011 ~ ~ ~ Cells2Society Summer Biomarkers Institute (3 days)\\
\strut ~ ~ ~ ~ ~ ~ ~ Center on Social Disparities in Health,
Northwestern University

2009 ~ ~ ~ Longitudinal Data Analysis (4 days)\\
\strut ~ ~ ~ ~ ~ ~ ~ Summer Statistics Institute, University of Texas at
Austin

2007 ~ ~ ~ National Institute on Aging Population Health and Aging
Program (8 weeks)\\
\strut ~ ~ ~ ~ ~ ~ ~ Demographic Research Laboratory, Western Washington
University

2006 ~ ~ ~ National Science Foundation Research Experience for
Undergraduates (10 weeks)\\
\strut ~ ~ ~ ~ ~ ~ ~ Population Research Center, University of Texas at
Austin

~

\section{Advising - Texas A\&M
University}\label{advising---texas-am-university}

\subsection{\texorpdfstring{\emph{Dissertation Committee
Chair}}{Dissertation Committee Chair}}\label{dissertation-committee-chair}

\setlength{\leftskip}{1cm}

Cynthia Cisneros Franco\\
JuYin Helen Wong

\setlength{\leftskip}{0cm}

\subsection{\texorpdfstring{\emph{Dissertation
Committee}}{Dissertation Committee}}\label{dissertation-committee}

\setlength{\leftskip}{1cm}

Nai Yu Chien\\
Nereyda Ortiz Osejo\\
Du Yi

\setlength{\leftskip}{0cm}

\subsection{\texorpdfstring{\emph{Preliminary Exams Committee
Chair}}{Preliminary Exams Committee Chair}}\label{preliminary-exams-committee-chair}

\setlength{\leftskip}{1cm}

Cynthia Cisneros Franco\\
JuYin Helen Wong

\setlength{\leftskip}{0cm}

\subsection{\texorpdfstring{\emph{Preliminary Exams
Committee}}{Preliminary Exams Committee}}\label{preliminary-exams-committee}

\setlength{\leftskip}{1cm}

Nai Yu Chien

\setlength{\leftskip}{0cm}

\section{Advising - Texas A\&M
University}\label{advising---texas-am-university-1}

\subsection{\texorpdfstring{\emph{Dissertation
Committee}}{Dissertation Committee}}\label{dissertation-committee-1}

\setlength{\leftskip}{1cm}

Nereyda Ortiz Osejo

\setlength{\leftskip}{0cm}

\subsection{\texorpdfstring{\emph{Master's Thesis
Chair}}{Master's Thesis Chair}}\label{masters-thesis-chair}

\setlength{\leftskip}{1cm}

Cynthia Cisneros Franco

\setlength{\leftskip}{0cm}

\section{Advising - University of
Memphis}\label{advising---university-of-memphis}

\subsection{\texorpdfstring{\emph{Master's Thesis
Chair}}{Master's Thesis Chair}}\label{masters-thesis-chair-1}

\setlength{\leftskip}{0.5cm}

Students completed and position after graduation

\setlength{\leftskip}{0cm}
\setlength{\leftskip}{1cm}

Purba Bhattacharjee (2024) -- PhD student, Dept of Sociology, University
of Tennessee\\
Samira Rahman (2024) - PhD student, Dept of Sociology University of
Oklahoma\\
Israt Jahan (2022) -- PhD student, Dept of Sociology, University of
Illinois, Urbana-\\
\strut ~~~~Champaign\\
Sarah Collins (2020) -- PhD student, Dept of Sociology, University of
Cincinnati\\
Aisha Naantaanbuu (2020) -- Digital Content Producer, WMC Action News
5\\
Kaniz Fatema (2019) -- PhD student, Dept of Sociology, University of
Iowa\\
Dontarious Cowans (2019) -- Data Analyst, RELY Workforce Group\\
Caleb Cooley (2018) -- PhD student, Dept of Sociology, Washington State
University\\
Daisy Angeles (2017) -- Bilingual Community Outreach Specialist, Freedom
Preparatory\\
\strut ~~~~Academy Charter Schools\\
Melissa Garcia-Dominguez (2017) -- PhD student, Dept of Sociology,
Indiana University

\setlength{\leftskip}{0cm}

\subsection{\texorpdfstring{\emph{Master's Thesis Committee
Member}}{Master's Thesis Committee Member}}\label{masters-thesis-committee-member}

\setlength{\leftskip}{0.5cm}

Students in progress

\setlength{\leftskip}{0cm}
\setlength{\leftskip}{1cm}

Golam Morshed\\
Fahima Sultana

\setlength{\leftskip}{0cm}

\setlength{\leftskip}{0.5cm}

Students completed and position after graduation

\setlength{\leftskip}{0cm}
\setlength{\leftskip}{1cm}

Fahima Sultana\\
Golam Morshed (2025) - PhD student, Department of Sociology, University
of Albany\\
Rifat Jahan Loran (2023) - PhD student, School of Urban Affairs and
Public Policy,\\
\strut ~~~~University of Memphis\\
Melissa Arismendy (2022) - Research Program Engagement Coordinator,
FiftyForward\\
Clarion Harris (2022)\\
Ebenezer Kpuinen (2021)\\
Uyvonda Stewart (2021) -- Adjunct Instructor, Dept of Sociology,
University of Memphis\\
Michael Topping (2020) -- PhD student, Dept of Sociology, University of
Wisconsin\\
Anna Church (2019) -- PhD student, Dept of Sociology, Ohio State
University\\
Hannah Pallotta (2019) -- Research Associate, Shelby County Schools\\
Samia Tasmim (2019) -- PhD student, Dept of Sociology, Stony Brook
University\\
Krista Wright Thayer (2018) -- PhD student, School of Urban Affairs and
Public Policy,\\
\strut ~~~~University of Memphis

\setlength{\leftskip}{0cm}

~

\section{Professional Service}\label{professional-service}

\underline{Reviewer}\\
\emph{American Journal of Sociology}, \emph{American Sociological
Review}, \emph{Annals of Epidemiology}, \emph{Biodemography and Social
Biology}, \emph{BMJ Open}, \emph{Demographic Research},
\emph{Demography}, \emph{Epidemiology}, \emph{Ethnicity and Health},
\emph{Innovations in Aging}, \emph{International Migration Review},
\emph{Journal of Aging and Health}, \emph{Journal of Gerontology: Series
B}, \emph{Journal of Health and Social Behavior}, \emph{Journal of
Immigrant and Minority Health}, \emph{Journal of Racial and Ethnic
Disparities}, \emph{Nicotine and Tobacco Research}, \emph{PLoS One},
\emph{Population Research and Policy Review}, \emph{Population Studies},
\emph{Research on Aging}, \emph{Social Currents}, \emph{Social Forces},
\emph{Social Science \& Medicine}, \emph{Social Science \&
Medicine--Population Health}, \emph{Social Science Research},
\emph{Sociological Quarterly}, \emph{Sociological Science},
\emph{Sociological Spectrum}, \emph{Sociology of Race and Ethnicity},
\emph{Socius}

\underline{Service to Texas A\&M University}\\
2025--present ~Executive Committee, Department of Sociology\\
2025--present ~Awards Committee, Department of Sociology\\
2024 ~ ~ ~ ~~ ~ ~ ~Chair, Faculty Search Committee (Demography and
Health), Department of\\
\strut ~ ~ ~ ~~ ~ ~ ~ ~ ~ ~ ~Sociology\\
2024--2025 ~ ~ ~Graduate Program and Evaluation Committee, Department of
Sociology

\underline{Service to University of Memphis}\\
2022--2024 ~ ~ ~ ~ Webmaster, Department of Sociology\\
2020--2024 ~ ~ ~ ~ Director of Graduate Studies, Department of
Sociology\\
2015--2024 ~ ~ ~ ~ Graduate Committee, Department of Sociology\\
2023 (fall) ~ ~ ~ ~ ~Member, Faculty Search Committee (Theory),
Department of Sociology\\
2023 (summer) ~Chair, Teaching Faculty Search Committee (two positions),
Department of\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~Sociology\\
2023 (spring) ~ ~ Comprehensive Exam Committee, Department of
Sociology\\
2022 (fall) ~ ~ ~ ~ ~Chair, Faculty Search Committee (Race), Department
of Sociology\\
2022 (summer) ~Postdoctoral Fellow Search Committee, Department of
Sociology\\
2021 ~ ~ ~ ~ ~ ~ ~ ~ ~Graduate Awards Sub-committee, Graduate Council\\
2021 (spring) ~ ~ Comprehensive Exam Committee, Department of
Sociology\\
2020 (fall) ~ ~ ~ ~ ~Comprehensive Exam Committee, Department of
Sociology\\
2020 (spring) ~ ~ Comprehensive Exam Committee, Department of
Sociology\\
2024 ~ ~ ~ ~ Chair, Faculty Search Committee (Demography and Health),
Department of Sociology\\
2024--present ~Graduate Program and Evaluation Committee, Department of
Sociology

\underline{Service to University of Memphis}\\
2022--2024 ~Webmaster, Department of Sociology\\
2020--2024 ~Director of Graduate Studies, Department of Sociology\\
2015--2024 ~Graduate Committee, Department of Sociology\\
2023 (fall) ~ ~ ~ Member, Faculty Search Committee (Theory), Department
of Sociology\\
2023 (summer) ~Chair, Teaching Faculty Search Committee (two positions),
Department of\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Sociology\\
2023 (spring) ~Comprehensive Exam Committee, Department of Sociology\\
2022 (fall) ~ ~ ~ Chair, Faculty Search Committee (Race), Department of
Sociology\\
2022 (summer) ~Postdoctoral Fellow Search Committee, Department of
Sociology\\
2021 ~ ~ ~ ~ ~ ~ ~ Graduate Awards Sub-committee, Graduate Council\\
2021 (spring) ~Comprehensive Exam Committee, Department of Sociology\\
2020 (fall) ~ ~ ~ Comprehensive Exam Committee, Department of
Sociology\\
2020 (spring) ~Comprehensive Exam Committee, Department of Sociology\\
2019 (summer) ~Postdoctoral Fellow Search Committee, Department of
Sociology\\
2018 (spring) ~ ~ Comprehensive Exam Committee, Department of
Sociology\\
2017 (fall) ~ ~ ~ ~ ~Faculty Search Committee (two tenure-track
positions), Department of\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~Sociology\\
2017 ~ ~ ~ ~ ~ ~ ~ ~ ~Session Moderator, National Conference on
Undergraduate Research\\
2016 (spring) ~ ~ Comprehensive Exam Committee, Department of Sociology

\underline{Service to Professional Organizations}\\
2026 ~ ~ ~ ~ ~ ~ ~ Chair, Outstanding Publication Award Committee,\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ American Sociological Association, Section
on Aging and the Life Course\\
2026 ~ ~ ~ ~ ~ ~ ~ Committee, Distinguished Contribution to Scholarship
in Population Award,\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ American Sociological Association, Section
on Sociology of Population\\
2026 ~ ~ ~ ~ ~ ~ ~ Program Committee on Mortality and Morbidity,\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2025 ~ ~ ~ ~ ~ ~ ~ President, Southern Demographic Association\\
2025--27 ~ ~ ~ ~ ~Memorial Service Committee, Population Association of
America\\
2024--27 ~ ~ ~ ~ ~Disseration Award Selection Committee, American
Sociological Association\\
2026 ~ ~ ~ ~ ~ ~ ~ Program Committee on Mortality and Morbidity,\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2025 ~ ~ ~ ~ ~ ~ ~ President, Southern Demographic Association\\
2025-27 ~ ~ ~ ~ ~Memorial Service Committee, Population Association of
America\\
2024-27 ~ ~ ~ ~ ~Disseration Award Selection Committee, American
Sociological Association\\
2022--present ~Webmaster, Southern Demographic Association\\
2021--23 ~ ~ ~ ~ ~Nominations Committee, Southern Sociological Society\\
2022--23 ~ ~ ~ ~ ~Program Committee, Section on Sociology of Population,
American Sociological\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Association\\
2022--23 ~ ~ ~ ~ ~Program Committee, Section on Aging and the Life
Course, American\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Sociological Association\\
2022--23 ~ ~ ~ ~ ~Program Committee, Section on Aging and the Life
Course, American Sociological\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Association\\
2021 ~ ~ ~ ~ ~ ~ ~ Program Committee and Chair of Sub-committee on
Mortality and Morbidity,\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2018--19 ~ ~ ~ ~ ~Student Paper Competition Committee, Southern
Demographic Association\\
2016--18 ~ ~ ~ ~ ~Member, Board of Directors, Southern Demographic
Association (three-year term)

\underline{Service to Academic Journals}\\
2024--present ~Associate Editor, \emph{Population Research and Policy
Review}\\
2024--present ~Editorial Board, \emph{Contexts}\\
2021--23 ~ ~ ~ ~ ~Editorial Board, \emph{Journal of Health and Social
Behavior}

\underline{Service to Discipline}\\
2026 ~ ~ ~ ~ ~ ~ ~ Session Organizer, ``Socioeconomic and Racial/Ethnic
Inequalities in Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2025 ~ ~ ~ ~ ~ ~ ~ Conference Organizer\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Demographic Association meeting\\
2024 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Population Aging''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Demographic Association meeting

\underline{Service to Discipline}\\
2024--present ~Associate Editor, \emph{Population Research and Policy
Review}\\
2024--present ~Editorial Board, \emph{Contexts}\\
2021--23 ~ ~ ~ ~ ~Editorial Board, \emph{Journal of Health and Social
Behavior}\\
2018--present ~Member, CenSoc Advisory Panel (PI: Joshua Goldstein, UC,
Berkeley)\\
2024 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Population Aging''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Demographic Association\\
2024 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Educational Inequality in Health and
Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2023 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Health and Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ American Sociological Association\\
2023 ~ ~ ~ ~ ~ ~ ~ Session Organizer, ``Health and Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ American Sociological Association\\
2023 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Gender Disparities in Health:
Mechanisms and Pathways''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America\\
2023 ~ ~ ~ ~ ~ ~ ~ Session Discussant, ``National/Subnational
Comparisons of COVID-19 Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America\\
2022 ~ ~ ~ ~ ~ ~ ~ Session Co-Chair, ``Biosocial Approaches to
Population Health''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America\\
2022 ~ ~ ~ ~ ~ ~ ~ Session Co-Chair, ``Old Wine in New Bottles: Tools
for Applied Demographers''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America\\
2021 ~ ~ ~ ~ ~ ~ ~ Session Presider, ``Morbidity and Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ American Sociological Association meeting\\
2021 ~ ~ ~ ~ ~ ~ ~ Session Organizer, ``Morbidity and Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ American Sociological Association meeting\\
2021 ~ ~ ~ ~ ~ ~ ~ Session Discussant, ``Immigration, Health, and Social
Context''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2021 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Socioeconomic Status and Mortality
in Europe''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2021 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Smoking, Health, and Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2021 ~ ~ ~ ~ ~ ~ ~ Session Presider, ``Health Policy''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Sociological Society meeting
(virtual)\\
2021 ~ ~ ~ ~ ~ ~ ~ Session Organizer, ``Smoking, Health, and
Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2020 ~ ~ ~ ~ ~ ~ ~ Session Discussant, ``Maternal Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting
(canceled due to COVID-19)\\
2020 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Smoking, Health, and Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting
(canceled due to COVID-19)\\
2020 ~ ~ ~ ~ ~ ~ ~ Session Organizer, ``Smoking, Health, and
Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting
(canceled due to COVID-19)\\
2019 ~ ~ ~ ~ ~ ~ ~ Session Discussant, ``Migration and
Health/Well-being''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2018 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Causes of Infant and Neonatal
Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Demographic Association meeting\\
2018 ~ ~ ~ ~ ~ ~ ~ Session Discussant, ``Race, Ethnicity, and Population
Health''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2018 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Disparities in Birth Outcomes in the
U.S.''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2018--21 ~ ~ ~ ~ ~Member, CenSoc Advisory Panel (PI: Joshua Goldstein,
UC, Berkeley)\\
2017 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Health and Maternal Behaviors''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Demographic Association meeting\\
2017 ~ ~ ~ ~ ~ ~ ~ Poster Session Judge, ``Health and Mortality 3''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Population Association of America meeting\\
2016 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Latino/a Health''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Demographic Association meeting\\
2015 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Race/Ethnic Differences in
Mortality''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Demographic Association meeting\\
2013 ~ ~ ~ ~ ~ ~ ~ Session Chair, ``Aging Populations in the United
States, Japan, and Korea''\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Southern Demographic Association meeting\\
2013 ~ ~ ~ ~ ~ ~ ~ Program Committee, 2013 REVES Network meeting\\
2010--13 ~ ~ ~ ~ ~Graduate Student Mentor, National Science Foundation
Research Experience for\\
\strut ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ Undergraduates\\
2010 ~ ~ ~ ~ ~ ~ ~ Program Committee, Southern Demographic Association\\
2010 ~ ~ ~ ~ ~ ~ ~ Local Arrangements Committee, Population Association
of America

~

\section{Professional Memberships}\label{professional-memberships}

American Sociological Association, 2005--present

\setlength{\leftskip}{0.75cm}

\emph{Sections:} Sociology of Population; Aging and the Life Course;
Medical Sociology

\setlength{\leftskip}{0cm}

Population Association of America, 2008--present\\
Southern Demographic Association, 2006--present\\
Southern Sociological Society, 2007--present

~

\section{References}\label{references}

Robert A. Hummer, Ph.D.\\
Howard W. Odum Professor of Sociology\\
University of North Carolina at Chapel Hill\\
206 West Franklin Street, Room 211\\
Chapel Hill, NC 27516\\
\href{mailto:rhummer@email.unc.edu}{\nolinkurl{rhummer@email.unc.edu}}

Mark D. Hayward, Ph.D.\\
Professor of Sociology and\\
Centennial Commission Professor of Liberal Arts\\
University of Texas at Austin\\
305 East 23rd Street, G1800\\
Austin, TX 78712\\
\href{mailto:mhayward@prc.utexas.edu}{\nolinkurl{mhayward@prc.utexas.edu}}

Anna Mueller, Ph.D.\\
Luther Dana Waterman Associate Professor of Sociology\\
Indiana University\\
Ballantine Hall 764\\
Bloomington, IN 47405\\
\href{mailto:mueller1@iu.edu}{\nolinkurl{mueller1@iu.edu}}

\end{document}
